SunPy - Python for Solar Physics

### 2014-08-26 4-Util.tex
fix for issue #122

\subsection{Sun}\label{ssec:util:sun}
The purpose of the \texttt{sun} subpackage is to provide solar-specific data such as ephemerides and
solar constants. The main namespace contains a number of functions that provide solar
ephemerides such as the Sun-to-Earth distance, solar-cycle number, the mean 
anomaly, etc.
All of these functions take a time as their input, which can be provided in a format
compatible with \texttt{sunpy.time.parse\_time()}.

The \texttt{sun.constants} module provides a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values within SunPy, but also to the user. Every solar 
constant is provided as a \texttt{Constant} object as defined by the Astropy \texttt{units} package. Each 
\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
the constant's provenance (i.e., reference) and its uncertainty. Using 
Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modeled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

>>>>

\subsection{Solar Constants and units}\label{ssec:util:sun}
Physical quantities (i.e. a number associated with a unit) are an important part
of scientific data analysis. SunPy makes use of the \texttt{Quantity} object provided by 
Astropy \texttt{units} package. This object maintains the relationship between 
a number and its unit and makes it easy to convert between units. 
As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers. Using proper
quantities inside of the code base also makes it easier to catch errors in calculations.
SunPy is currently working on integrating quantities throughout the code base.
In order to encourage the use of units and to enable consistency SunPy provides
the \texttt{sun} subpackage which includes solar-specific data such as ephemerides and
solar constants. The main namespace contains a number of functions that provide solar
ephemerides such as the Sun-to-Earth distance, solar-cycle number, mean 
anomaly, etc.
All of these functions take a time as their input, which can be provided in a format
compatible with \texttt{sunpy.time.parse\_time()}.

The \texttt{sunpy.sun.constants} module provides a number of solar-related 
constants in order to enable the calculation of derived solar 
values within SunPy, but also to the user. All solar 
constant are provided as \texttt{Constant} objects as defined in the Astropy \texttt{units} package. Each 
\texttt{Constant} object defines a \texttt{Quantity}, along with 
the constant's provenance (i.e., reference) and its uncertainty. The use of this package
is shown in Listing~\ref{code:constants_code}.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modeled on that provided by the SciPy \texttt{constants}
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.
